\documentclass[a4paper]{exam}

\usepackage{amsmath,amssymb, amsthm}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{titling}



% Header and footer.
\pagestyle{headandfoot}
\runningheadrule
\runningfootrule
\runningheader{CS/MATH 113, SPRING 2025}{Pset 01: Propositional Logic}{\theauthor}
\runningfooter{}{Page \thepage\ of \numpages}{}
\firstpageheader{}{}{}

% \printanswers %Uncomment this line

\title{Problem Set 01: Propositional logic}
\author{Blingblong} % <=== replace with your student ID, e.g. xy012345
\date{CS/MATH 113 Discrete Mathematics\\Habib University\\Spring 2025}

\qformat{{\large\bf \thequestion. \thequestiontitle}\hfill}
\boxedpoints

\begin{document}
\maketitle

\begin{questions}
    \titledquestion{Parkour Civilization}
    Let proposition $p$ and $q$ be:
    \begin{itemize}
        \item $p$: I would jump 1 block for raw chicken.
        \item $q$: I am a parkour noob.
    \end{itemize}
    Express each of these compound propositions as an English sentence.
    \begin{parts}
        \part $\neg q \lor (\neg p \land q)$
        \begin{solution}
            % Enter solution here
        \end{solution}

        \part $\neg q \implies \neg p$
        \begin{solution}
            % Enter solution here
        \end{solution}
    \end{parts}

    \titledquestion{Jump off kick back spin for hours}
    Let proposition $p$ and $q$ be:
    \begin{itemize}
        \item $p$: I have an elemental weapon.
        \item $q$: I am a master of spinjitzu. 
    \end{itemize}
    \begin{parts}
        \part Either I have an elemental weapon or I am a master of spinjitzu, but I don't have an elemental weapon if I am a master of spinjitzu.
        \begin{solution}
            % Enter solution here
        \end{solution}

        \part Having an elemental weapon is necessary and sufficient for it to be a master of spinjitzu.
        \begin{solution}
            % Enter solution here
        \end{solution}
    \end{parts}


    \titledquestion{Jojo part 7 battle in egypt arc} You're a bizarre adventure with Johnny Joestar to stop the president of the United States. You need to find pieces of the corpse of a saint.
    The adventure leads you to an island. 
    Gyro Zeppeli tells you that a piece is in a cave. The cave is guarded by two enemy stand users \emph{Radiohead} and \emph{Nirvana}, who are inhabitants of the island. One always lies and other always tells the truth.
    They will only let you into the cave if you can determine, if possible, what \emph{Radiohead} and \emph{Nirvana} are if they address you in the ways described.
    \emph{Radiohead} says ``The two of us both always tells the truth'' and \emph{Nirvana} says ``\emph{Radiohead} always lie''.
    \begin{solution}
        % Enter solution here
    \end{solution}

    \titledquestion{Khud sey hosakey Milaap} 
    Show that the absorption laws holds 
    \begin{parts}
        \part $p\lor (p\land q) \equiv p$
        \begin{solution}
            % Enter solution here
        \end{solution}

        \part $p\land (p\lor q) \equiv p$
        \begin{solution}
            % Enter solution here
        \end{solution}
    \end{parts}
    

    \titledquestion{Is it true?} Determine whether $(\neg p \land (p \implies q)) \implies \neg q$ is a tautology.
    \begin{solution}
        % Enter solution here
    \end{solution}


      
\end{questions}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
